---
title: "TFMseg_example"
author: "yuqi"
date: "2026-08-07"
output: html_document
---

# Functions and packages

This example file corresponds to the simulation setting considered in https://arxiv.org/pdf/2604.11300.

```{r}
r_files <- list.files("/Users/yuqi/Documents/GitHub/TFMseg/Method_funcs", pattern = "\\.R$", full.names = TRUE)
for (f in r_files) source(f)

library(tensorMiss)
library(rTensor)
library(RTFA)
library(ggplot2)
library(dplyr)
library(tidyr)
library(kableExtra)
library(lubridate)
library(knitr)
library(scales)
```


# Data example

This dataset provides one example under (S1) in the paper, where a single mode changes at each change point. We set $T = 1600$, $K = 3$, $p = (p1, p2, p3) = (10, 10, 10)$, $r = (r1, r2, r3) = (3, 3, 3)$. The true change points are located at $(\theta_1, \theta_2, \theta_3) = (400, 800, 1200)$, with serial correlation $rho_f = 0.7$.

```{r}
Time <- 1600
theta_coef <- c(0.25, 0.5, 0.75)
theta <- floor(Time * theta_coef)
theta <- sort(unique(theta[theta > 0 & theta < Time]))

setting_args <- make_tensor_setting(
      data_setting = "s1",
      theta = theta,
      dim_latent = c(3,3,3))

true_cp <- setting_args$true_cp
m_true <- length(true_cp)
    
data_sim <- dgp_general(
  model = "tensor",
  dim_obs = c(10,10,10),
  dim_latent = c(3,3,3),
  Time = Time,
  dep = TRUE,
  coeff = 0.7,
  true_cp = true_cp,
  type_mode = setting_args$type_mode,
  type_change = setting_args$type_change,
  shift_ind = setting_args$shift_ind,
  shift_mean = setting_args$shift_mean,
  shift_var = setting_args$shift_var,
  transform_list = setting_args$transform_list,
  add_factors = setting_args$add_factors,
  add_factors_coeff = setting_args$add_factors_coeff,
  dist = "Gaussian",
  idio_coeff = FALSE
)
```


```{r}
data_example <- readRDS("/Users/yuqi/Documents/GitHub/TFMseg/Method_funcs/data_example.rds")
X <- data_example$X
```


# Loading and factor estimation

See Section~3.1, we use a one-step projection estimation.
```{r}
# input X of dimension p1 x p2 x ... x pK x T
K <- length(dim(X)) - 1L # number of modes
dim_X <- dim(X)[seq_len(K)] # p1 x p2 x ... x pK

# one-step projection estimation for time invariant loadings and pseudo-factor
est_load <- global_pca(X = X, dim_X = dim_X, r_hat = NULL) # for unknown factor numbers
r_hat <- est_load$r_hat # estimated factor numbers
Lambda_1 <- est_load$Lambda_proj$Lambda_proj_mode1 # estimated loading for mode 1, of dim p1 x r1
G <- est_load$G_proj # estimated pseudo-factor time series, of dim r1 x r2 x r3
G_dim <- as.vector(est_load$r_hat) # estimated pseudo-factor dim, r1 x r2 x r3
```


# Change point detection

Change point detection is implemented based on Algorithm~1 of the paper.

The function TFMseg() uses global long-run covariance standardisation, as described in Section~3.3. By default, trim = floor(0.25 * T / log(T)) throughout. The default detection threshold is calibrated as Section~C.1

```{r}
out <- TFMseg(G = G, G_dim = G_dim, trim = NULL)
out$est.cp
```

We additionally consider a version using interval-wise HAC long-run covariance estimation

```{r}
out_local_lrv <- TFMseg_local_lrv(G = G, G_dim = G_dim, trim = NULL)
out_local_lrv$est.cp
```



# Mode-identification

Mode identification is implemented based on Eq.(3.3) of the paper and takes the previously estimated change points as input. We report the results under both global and local long-run covariance standardisation. The default identification threshold is calibrated as Section~C.2.

Using change points estimated under global long-run covariance standardisation:

```{r}
out_modes <- id_modes(G = G, G_dim = G_dim, dim_obs = dim_X, cp_vec = out$est.cp, id_thd_coef = NULL)
out_modes$changed
```

```{r}
out_modes_local_lrv <- id_modes(G = G, G_dim = G_dim, dim_obs = dim_X, cp_vec = out_local_lrv$est.cp, id_thd_coef = NULL)
out_modes_local_lrv$changed
```

