---
title: "examples"
author: "yuqi"
date: "2026-03-07"
output: html_document
---

# Detection

## S0 + dependence

```{r}
tab_s0 <- simu_ret(methods = c("TFMseg", "LR"), 
                  dim_obs_list = list(c(10,10,10), c(20,20,20), c(10,20,40), c(10,10,100)),
                  Time_list = c(400, 800, 1600, 3200),
                  data_setting = "s0", dep = TRUE, theta_coef = c(0,0,0))
tab_s0$table
```

## S0 + independence

```{r}
tab_s0_indep <- simu_ret(methods = c("TFMseg", "LR"), 
                  dim_obs_list = list(c(10,10,10), c(20,20,20), c(10,20,40), c(10,10,100)),
                  Time_list = c(400, 800, 1600, 3200),
                  data_setting = "s0", dep = FALSE, theta_coef = c(0,0,0))
tab_s0_indep$table
```

## S1 + equal + dependence

```{r}
tab_s1_eq <- simu_ret(methods = c("TFMseg", "oraclePZW", "LR"), 
                  dim_obs_list = list(c(10,10,10), c(20,20,20), c(10,20,40), c(10,10,100)),
                  Time_list = c(400, 800, 1600, 3200),
                  data_setting = "s1", dep = TRUE, theta_coef = c(0.25,0.5,0.75))
tab_s1_eq$table

tab_s1_eq_good <- extract_accurate(tab_s1_eq, 
                                   source_names = c("TFMseg","oraclePZW", "LR"), q = 3)

multi_hist_subplot(
  tab_s1_eq, # all
  tab_s1_eq_good, # filtered
  Time_list = c(400, 800, 1600, 3200),
  dim_obs_list =  list(c(10,10,10), c(20,20,20), c(10,20,40), c(10,10,100)),
  theta_coef = c(0.25, 0.5, 0.75),
  source_names = c("TFMseg","oraclePZW", "LR"),
  compare_dataset = TRUE,
  dataset_names = c("All", "Exact 3"),
  setting = "S1")
```

## S1 + equal + independence

```{r}
tab_s1_eq_indep <- simu_ret(methods = c("TFMseg", "oraclePZW", "LR"), 
                  dim_obs_list = list(c(10,10,10), c(20,20,20), c(10,20,40), c(10,10,100)),
                  Time_list = c(400, 800, 1600, 3200),
                  data_setting = "s1", dep = FALSE, theta_coef = c(0.25,0.5,0.75))
tab_s1_eq_indep$table

tab_s1_eq_indep_good <- extract_accurate(tab_s1_eq_indep, 
                                   source_names = c("TFMseg","oraclePZW", "LR"), q = 3)

multi_hist_subplot(
  tab_s1_eq_indep, # all
  tab_s1_eq_indep_good, # filtered
  Time_list = c(400, 800, 1600, 3200),
  dim_obs_list =  list(c(10,10,10), c(20,20,20), c(10,20,40), c(10,10,100)),
  theta_coef = c(0.25, 0.5, 0.75),
  source_names = c("TFMseg","oraclePZW", "LR"),
  compare_dataset = TRUE,
  dataset_names = c("All", "Exact 3"),
  setting = "S1")
```

## S1 + unequal + dependence

```{r}
tab_s1_uneq <- simu_ret(methods = c("TFMseg", "oraclePZW", "LR"), 
                  dim_obs_list = list(c(10,10,10), c(20,20,20), c(10,20,40), c(10,10,100)),
                  Time_list = c(400, 800, 1600, 3200),
                  data_setting = "s1", dep = TRUE, theta_coef = c(0.25,0.5,0.625))
tab_s1_uneq$table

tab_s1_uneq_good <- extract_accurate(tab_s1_uneq, 
                                   source_names = c("TFMseg","oraclePZW", "LR"), q = 3)

multi_hist_subplot(
  tab_s1_uneq, # all
  tab_s1_uneq_good, # filtered
  Time_list = c(400, 800, 1600, 3200),
  dim_obs_list =  list(c(10,10,10), c(20,20,20), c(10,20,40), c(10,10,100)),
  theta_coef = c(0.25, 0.5, 0.625),
  source_names = c("TFMseg","oraclePZW", "LR"),
  compare_dataset = TRUE,
  dataset_names = c("All", "Exact 3"),
  setting = "S1")
```

## S1 + unequal + independence

```{r}
tab_s1_uneq_indep <- simu_ret(methods = c("TFMseg", "oraclePZW", "LR"), 
                  dim_obs_list = list(c(10,10,10), c(20,20,20), c(10,20,40), c(10,10,100)),
                  Time_list = c(400, 800, 1600, 3200),
                  data_setting = "s1", dep = FALSE, theta_coef = c(0.25,0.5,0.625))
tab_s1_uneq_indep$table

tab_s1_uneq_indep_good <- extract_accurate(tab_s1_uneq_indep, 
                                   source_names = c("TFMseg","oraclePZW", "LR"), q = 3)

multi_hist_subplot(
  tab_s1_uneq_indep, # all
  tab_s1_uneq_indep_good, # filtered
  Time_list = c(400, 800, 1600, 3200),
  dim_obs_list =  list(c(10,10,10), c(20,20,20), c(10,20,40), c(10,10,100)),
  theta_coef = c(0.25, 0.5, 0.625),
  source_names = c("TFMseg","oraclePZW", "LR"),
  compare_dataset = TRUE,
  dataset_names = c("All", "Exact 3"),
  setting = "S1")
```


## S2 + equal + dependence

```{r}
tab_s2_eq <- simu_ret(methods = c("TFMseg", "oraclePZW", "LR"), 
                  dim_obs_list = list(c(10,10,10), c(20,20,20), c(10,20,40), c(10,10,100)),
                  Time_list = c(400, 800, 1600, 3200),
                  data_setting = "s2", dep = TRUE, theta_coef = c(0.25,0.5,0.75))
tab_s2_eq$table

tab_s2_eq_good <- extract_accurate(tab_s2_eq, 
                                   source_names = c("TFMseg","oraclePZW", "LR"), q = 3)

multi_hist_subplot(
  tab_s2_eq, # all
  tab_s2_eq_good, # filtered
  Time_list = c(400, 800, 1600, 3200),
  dim_obs_list =  list(c(10,10,10), c(20,20,20), c(10,20,40), c(10,10,100)),
  theta_coef = c(0.25, 0.5, 0.75),
  source_names = c("TFMseg","oraclePZW", "LR"),
  compare_dataset = TRUE,
  dataset_names = c("All", "Exact 3"),
  setting = "S2")
```

## S2 + equal + independence

```{r}
tab_s2_eq_indep <- simu_ret(methods = c("TFMseg", "oraclePZW", "LR"), 
                  dim_obs_list = list(c(10,10,10), c(20,20,20), c(10,20,40), c(10,10,100)),
                  Time_list = c(400, 800, 1600, 3200),
                  data_setting = "s2", dep = FALSE, theta_coef = c(0.25,0.5,0.75))
tab_s2_eq_indep$table

tab_s2_eq_indep_good <- extract_accurate(tab_s2_eq_indep, 
                                   source_names = c("TFMseg","oraclePZW", "LR"), q = 3)

multi_hist_subplot(
  tab_s2_eq_indep, # all
  tab_s2_eq_indep_good, # filtered
  Time_list = c(400, 800, 1600, 3200),
  dim_obs_list =  list(c(10,10,10), c(20,20,20), c(10,20,40), c(10,10,100)),
  theta_coef = c(0.25, 0.5, 0.75),
  source_names = c("TFMseg","oraclePZW", "LR"),
  compare_dataset = TRUE,
  dataset_names = c("All", "Exact 3"),
  setting = "S2")
```

## S2 + unequal + dependence

```{r}
tab_s2_uneq <- simu_ret(methods = c("TFMseg", "oraclePZW", "LR"), 
                  dim_obs_list = list(c(10,10,10), c(20,20,20), c(10,20,40), c(10,10,100)),
                  Time_list = c(400, 800, 1600, 3200),
                  data_setting = "s2", dep = TRUE, theta_coef = c(0.25,0.5,0.625))
tab_s2_uneq$table

tab_s2_uneq_good <- extract_accurate(tab_s2_uneq, 
                                   source_names = c("TFMseg","oraclePZW", "LR"), q = 3)

multi_hist_subplot(
  tab_s2_uneq, # all
  tab_s2_uneq_good, # filtered
  Time_list = c(400, 800, 1600, 3200),
  dim_obs_list =  list(c(10,10,10), c(20,20,20), c(10,20,40), c(10,10,100)),
  theta_coef = c(0.25, 0.5, 0.625),
  source_names = c("TFMseg","oraclePZW", "LR"),
  compare_dataset = TRUE,
  dataset_names = c("All", "Exact 3"),
  setting = "S2")
```

## S2 + unequal + independence

```{r}
tab_s2_uneq_indep <- simu_ret(methods = c("TFMseg", "oraclePZW", "LR"), 
                  dim_obs_list = list(c(10,10,10), c(20,20,20), c(10,20,40), c(10,10,100)),
                  Time_list = c(400, 800, 1600, 3200),
                  data_setting = "s2", dep = FALSE, theta_coef = c(0.25,0.5,0.625))
tab_s2_uneq_indep$table

tab_s2_uneq_indep_good <- extract_accurate(tab_s2_uneq_indep, 
                                   source_names = c("TFMseg","oraclePZW", "LR"), q = 3)

multi_hist_subplot(
  tab_s2_uneq_indep, # all
  tab_s2_uneq_indep_good, # filtered
  Time_list = c(400, 800, 1600, 3200),
  dim_obs_list =  list(c(10,10,10), c(20,20,20), c(10,20,40), c(10,10,100)),
  theta_coef = c(0.25, 0.5, 0.625),
  source_names = c("TFMseg","oraclePZW", "LR"),
  compare_dataset = TRUE,
  dataset_names = c("All", "Exact 3"),
  setting = "S2")
```

# Identification

## S1 + equal + dependence

```{r}
id_s1_eq <- id_modes_1(cp_est_df = tab_s1_eq_good$cp_est_df,
                        dim_obs_list = list(c(10,10,10), c(20,20,20), c(10,20,40), c(10,10,100)),
                        Time_list = c(400, 800, 1600, 3200),
                        dim_latent  = c(3,3,3),
                        theta_coef  = c(0.25,0.5,0.75),
                        r_hat = NULL,
                        trim_len = 1,
                        use_true_cp = FALSE,
                        data_setting = "s1")


eval_all(id_s1_eq, id_thd_coef = 3.8, true_mode_list = list(c(1), c(2), c(3)))
```

## S1 + equal + independence

```{r}
id_s1_eq_indep <- id_modes_1(cp_est_df = tab_s1_eq_indep_good$cp_est_df,
                        dim_obs_list = list(c(10,10,10), c(20,20,20), c(10,20,40), c(10,10,100)),
                        Time_list = c(400, 800, 1600, 3200),
                        dim_latent  = c(3,3,3),
                        theta_coef  = c(0.25,0.5,0.75),
                        r_hat = NULL,
                        trim_len = 1,
                        use_true_cp = FALSE,
                        data_setting = "s1")


eval_all(id_s1_eq_indep, id_thd_coef = 3.8, true_mode_list = list(c(1), c(2), c(3)))
```



## S1 + unequal + dependence

```{r}
id_s1_uneq <- id_modes_1(cp_est_df = tab_s1_uneq_good$cp_est_df,
                        dim_obs_list = list(c(10,10,10), c(20,20,20), c(10,20,40), c(10,10,100)),
                        Time_list = c(400, 800, 1600, 3200),
                        dim_latent  = c(3,3,3),
                        theta_coef  = c(0.25,0.5,0.625),
                        r_hat = NULL,
                        trim_len = 1,
                        use_true_cp = FALSE,
                        data_setting = "s1")


eval_all(id_s1_uneq, id_thd_coef = 3.8, true_mode_list = list(c(1), c(2), c(3)))
```

## S1 + unequal + independence

```{r}
id_s1_uneq_indep <- id_modes_1(cp_est_df = tab_s1_uneq_indep_good$cp_est_df,
                        dim_obs_list = list(c(10,10,10), c(20,20,20), c(10,20,40), c(10,10,100)),
                        Time_list = c(400, 800, 1600, 3200),
                        dim_latent  = c(3,3,3),
                        theta_coef  = c(0.25,0.5,0.625),
                        r_hat = NULL,
                        trim_len = 1,
                        use_true_cp = FALSE,
                        data_setting = "s1")


eval_all(id_s1_uneq_indep, id_thd_coef = 3.8, true_mode_list = list(c(1), c(2), c(3)))
```

## S2 + equal + dependence

```{r}
id_s2_eq <- id_modes_1(cp_est_df = tab_s2_eq_good$cp_est_df,
                        dim_obs_list = list(c(10,10,10), c(20,20,20), c(10,20,40), c(10,10,100)),
                        Time_list = c(400, 800, 1600, 3200),
                        dim_latent  = c(3,3,3),
                        theta_coef  = c(0.25,0.5,0.75),
                        r_hat = NULL,
                        trim_len = 1,
                        use_true_cp = FALSE,
                        data_setting = "s2")


eval_all(id_s2_eq, id_thd_coef = 3.8, true_mode_list = list(c(1), c(2), c(2,3)))
```

## S2 + equal + independence

```{r}
id_s2_eq_indep <- id_modes_1(cp_est_df = tab_s2_eq_indep_good$cp_est_df,
                        dim_obs_list = list(c(10,10,10), c(20,20,20), c(10,20,40), c(10,10,100)),
                        Time_list = c(400, 800, 1600, 3200),
                        dim_latent  = c(3,3,3),
                        theta_coef  = c(0.25,0.5,0.75),
                        r_hat = NULL,
                        trim_len = 1,
                        use_true_cp = FALSE,
                        data_setting = "s2")


eval_all(id_s2_eq_indep, id_thd_coef = 3.8, true_mode_list = list(c(1), c(2), c(2,3)))
```



## S2 + unequal + dependence

```{r}
id_s2_uneq <- id_modes_1(cp_est_df = tab_s2_uneq_good$cp_est_df,
                        dim_obs_list = list(c(10,10,10), c(20,20,20), c(10,20,40), c(10,10,100)),
                        Time_list = c(400, 800, 1600, 3200),
                        dim_latent  = c(3,3,3),
                        theta_coef  = c(0.25,0.5,0.625),
                        r_hat = NULL,
                        trim_len = 1,
                        use_true_cp = FALSE,
                        data_setting = "s2")


eval_all(id_s2_uneq, id_thd_coef = 3.8, true_mode_list = list(c(1), c(2), c(2,3)))
```

## S2 + unequal + independence

```{r}
id_s2_uneq_indep <- id_modes_1(cp_est_df = tab_s2_uneq_indep_good$cp_est_df,
                        dim_obs_list = list(c(10,10,10), c(20,20,20), c(10,20,40), c(10,10,100)),
                        Time_list = c(400, 800, 1600, 3200),
                        dim_latent  = c(3,3,3),
                        theta_coef  = c(0.25,0.5,0.625),
                        r_hat = NULL,
                        trim_len = 1,
                        use_true_cp = FALSE,
                        data_setting = "s2")


eval_all(id_s2_uneq_indep, id_thd_coef = 3.8, true_mode_list = list(c(1), c(2), c(2,3)))
```


# Mode-informed estimation

```{r}
MI_reest <- simu_reest(
  Time_list = c(400, 800, 1600, 3200)[1],
  dim_obs_list = list(c(10,10,10), c(10,10,100), c(10,100,10), c(100,10,10))[1],
  dim_latent = c(3, 3, 3),
  dep = FALSE,
  theta_coef = 0.5,
  use_true_cp = FALSE
)
```

```{r}
plot_reest_box(
  reest_obj = MI_reest,
  Time_select = 400,
  dim_obs_list = list(c(10, 10, 10), c(10, 10, 100), c(10,100,10), c(100,10,10), c(100,10,10)),
  y_lim = c(0,0.05),
  title_suffix = "T = 400, using estimated factor numbers",
  legend_labels = c("Segment pre", "Segment post", "Mode-informed")
)
```


```{r}
plot_reest_box_all_mode(
  reest_obj = MI_reest,
  Time_list = c(400, 800, 1600, 3200),
  dim_obs_list = list(
    c(10, 10, 10),
    c(10, 10, 100),
    c(10, 100, 10),
    c(100, 10, 10)
  ),
  y_lim = list(c(0, 0.05), c(0, 0.03), c(0, 0.03), c(0, 0.02)),
  title_suffix = "All modes: using estimated factor numbers",
  legend_labels = c("Segment pre", "Segment post", "Mode-informed")
)
```


# Detection with missingness

## S1 + equal + dependence + missingness

```{r}
miss_tab_s1_eq <- simu_ret(methods = "TFMseg", 
                  dim_obs_list = list(c(10,10,10), c(20,20,20), c(10,20,40), c(10,10,100)),
                  Time_list = c(400, 800, 1600, 3200),
                  data_setting = "s1", dep = TRUE, theta_coef = c(0.25,0.5,0.75),
                  miss = TRUE)
miss_tab_s1_eq$table

miss_tab_s1_eq_good <- extract_accurate(miss_tab_s1_eq, 
                                   source_names = "TFMseg", q = 3)

multi_hist_subplot_method(
  complete_1 = tab_s1_eq,
  extract_1 = tab_s1_eq_good,
  complete_2 = miss_tab_s1_eq,
  extract_2 = miss_tab_s1_eq_good,
  Time_list = c(400, 1600),
  theta_coef = c(0.25, 0.5, 0.75),
  dim_obs_list = list(c(10, 10, 10), c(10, 10, 100), c(10, 20, 40), c(20, 20, 20)),
  source_names = c("TFMseg"),
  scenario_names = c("Complete data", "Missingness"),
  dataset_names = c("All", "Exact 3"),
  dataset_alpha = 0.5,
  dataset_position = "identity",
  setting = "S1"
)
```

## S1 + equal + independence + missingness

```{r}
miss_tab_s1_eq_indep <- simu_ret(methods = "TFMseg", 
                  dim_obs_list = list(c(10,10,10), c(20,20,20), c(10,20,40), c(10,10,100)),
                  Time_list = c(400, 800, 1600, 3200),
                  data_setting = "s1", dep = FALSE, theta_coef = c(0.25,0.5,0.75),
                  miss = TRUE)
miss_tab_s1_eq_indep$table

miss_tab_s1_eq_indep_good <- extract_accurate(miss_tab_s1_eq_indep, 
                                   source_names = "TFMseg", q = 3)

multi_hist_subplot_method(
  complete_1 = tab_s1_eq_indep,
  extract_1 = tab_s1_eq_indep_good,
  complete_2 = miss_tab_s1_eq_indep,
  extract_2 = miss_tab_s1_eq_indep_good,
  Time_list = c(400, 1600),
  theta_coef = c(0.25, 0.5, 0.75),
  dim_obs_list = list(c(10, 10, 10), c(10, 10, 100), c(10, 20, 40), c(20, 20, 20)),
  source_names = c("TFMseg"),
  scenario_names = c("Complete data", "Missingness"),
  dataset_names = c("All", "Exact 3"),
  dataset_alpha = 0.5,
  dataset_position = "identity",
  setting = "S1"
)
```

## S1 + unequal + dependence + missingness

```{r}
miss_tab_s1_uneq <- simu_ret(methods = "TFMseg", 
                  dim_obs_list = list(c(10,10,10), c(20,20,20), c(10,20,40), c(10,10,100)),
                  Time_list = c(400, 800, 1600, 3200),
                  data_setting = "s1", dep = TRUE, theta_coef = c(0.25,0.5,0.625),
                  miss = TRUE)
miss_tab_s1_uneq$table

miss_tab_s1_uneq_good <- extract_accurate(miss_tab_s1_uneq, 
                                   source_names = "TFMseg", q = 3)

multi_hist_subplot_method(
  complete_1 = tab_s1_uneq,
  extract_1 = tab_s1_uneq_good,
  complete_2 = miss_tab_s1_uneq,
  extract_2 = miss_tab_s1_uneq_good,
  Time_list = c(400, 1600),
  theta_coef = c(0.25, 0.5, 0.625),
  dim_obs_list = list(c(10, 10, 10), c(10, 10, 100), c(10, 20, 40), c(20, 20, 20)),
  source_names = c("TFMseg"),
  scenario_names = c("Complete data", "Missingness"),
  dataset_names = c("All", "Exact 3"),
  dataset_alpha = 0.5,
  dataset_position = "identity",
  setting = "S1"
)
```

## S1 + unequal + independence + missingness

```{r}
miss_tab_s1_uneq_indep <- simu_ret(methods = "TFMseg", 
                  dim_obs_list = list(c(10,10,10), c(20,20,20), c(10,20,40), c(10,10,100)),
                  Time_list = c(400, 800, 1600, 3200),
                  data_setting = "s1", dep = FALSE, theta_coef = c(0.25,0.5,0.625),
                  miss = TRUE)
miss_tab_s1_uneq_indep$table

miss_tab_s1_uneq_indep_good <- extract_accurate(miss_tab_s1_uneq_indep, 
                                   source_names = "TFMseg", q = 3)

multi_hist_subplot_method(
  complete_1 = tab_s1_uneq_indep,
  extract_1 = tab_s1_uneq_indep_good,
  complete_2 = miss_tab_s1_uneq_indep,
  extract_2 = miss_tab_s1_uneq_indep_good,
  Time_list = c(400, 1600),
  theta_coef = c(0.25, 0.5, 0.625),
  dim_obs_list = list(c(10, 10, 10), c(10, 10, 100), c(10, 20, 40), c(20, 20, 20)),
  source_names = c("TFMseg"),
  scenario_names = c("Complete data", "Missingness"),
  dataset_names = c("All", "Exact 3"),
  dataset_alpha = 0.5,
  dataset_position = "identity",
  setting = "S1"
)
```

