---
title: "single_identify+detection_use"
output: pdf_document
author: Yuqi Zhang
date: "2025-06-13"
---

```{r}
scripts_to_source <- c(
  "TNotSBS.R",
  "global_est.R",
  "dgp_yuqi.R",
  "est_factor_number.R",
  "seeded_intervals.R",
  "mode_identify.R",
  "simulate_identify+detection.R"
)

sapply(scripts_to_source, source)
```


M <- diag(c(1, 1, 3))
M <- diag(c(1, 2, 3))
M <- diag(c(1, 2, 1, 1)) #NO, but 
M <- diag(4); M[1,2] <- 1; M <- t(M)%*%M #YES
M <- diag(c(1,2,3,2)) YES
M <- matrix(c(1, 1, 1,
               0, 1, 1,
               0, 0, 1), nrow = 3, byrow = TRUE)
M <- matrix(rnorm(4 * 4, mean = 0, sd = 1), nrow = 4, ncol = 4)
M <- matrix(rnorm(2 * 2, mean = 0, sd = 1), nrow = 2, ncol = 2)

M <- qr.Q(qr(matrix(rnorm(9), 3, 3))) 
M <- diag(c(3, 3, 3))
M <- matrix(c(1, 2, 3,
               0, 4, 5,
               0, 0, 6), nrow = 3, byrow = TRUE)
M <- matrix(c(1, 2, 3,
               0, 4, 5,
               0, 0, 0), nrow = 3, byrow = TRUE)
               
# single change - one realisation - only identify

```{r}
res <- dgp_general(
  model= "matrix",
  dim_obs = c(100, 100),
  dim_latent = c(3, 3),
  Time = 500,
  coeff = 0.7,
  true_cp = 250,
  type_mode = list(c(1)),
  type_change = list("l"),
  transform_list = list(list(M, NULL))
)

X <- res$X
K <- length(dim(X)) - 1
dim_obs <- dim(X)[1:K]

idt <- mode_identify(X, dim_obs, cp=250, st= 1, ed= dim(X)[length(dim_obs) + 1])
idt
```

# single change - one realisation - only detection

```{r}
res_est <- gloal_pca(X, dim_obs)
G <- res_est$G
G_dim <- as.vector(res_est$r_hat)
cand_sbs(G, G_dim, V.diag = TRUE, lrv = TRUE, n = NULL, lbd = NULL, single = TRUE)
```

# single change - with repetition - identify + detection

```{r}
single_identify_detection(M,
                          dim_obs = c(100, 100),
                          dim_latent = c(3, 3),
                          TT = 500,
                          true_cp = 500 / 2,
                          true_mode = 1,
                          reps = 100,
                          seed = 1,
                          detection = TRUE)
```


# Multiple changes

```{r}
# matrix 2 changes
res <- dgp_general(
  model= "matrix",
  dim_obs = c(100, 100),
  dim_latent = c(4, 3),
  Time = 1000,
  coeff = 0.1,
  true_cp = c(200, 600),
  type_mode = list(c(1),    c(2)),
  type_change = list("l", "f"),
  shift_ind = list(list(c(80,2), NULL),
                           list(NULL, NULL)),
  shift_mean = c(10, 0),
  shift_var = c(2^2, 0),
  add_factors = list(c(0, 0),  c(0, 2)),
  add_factors_coeff = list(c(0, 0),  c(0, 0.1))
)

X <- res$X
Time <- dim(X)[3]
dim_X <- dim(X)[1:2]

res_load <- gloal_pca(X, dim_X)
G <- res_load$G
G_dim <- as.vector(res_load$r_hat)

candidates <- cand_sbs(G, G_dim, single = FALSE)
TNotSBS(G, G_dim, method = c("oracle"), m = 2)
```



```{r}
res <- dgp_general(
  model = "tensor",
  dim_obs = c(50, 50, 100),
  dim_latent  = c(2, 2, 3),
  Time = 200,
  coeff = 0.5,
  true_cp = c(50, 75, 150),
  type_mode = list(c(1), c(2), c(2,3)),
  type_change = list("l", "f", c("l", "f")),
  shift_ind = list(list(c(40,1), NULL, NULL),
                           list(NULL, NULL, NULL), 
                           list(NULL, c(20,2), NULL)),
  shift_mean = c(1, 0, 2),
  shift_var = c(2^2, 0, 1^2),
  add_factors = list(c(0, 0, 0),  c(0, 1, 0), c(0, 0, 3)),
  add_factors_coeff = list(c(0, 0, 0),  c(0, 0.3, 0), c(0, 0, 0.4))
)

X <- res$X
Time <- dim(X)[4]
dim_X <- dim(X)[1:3]

res_load <- gloal_pca(X, dim_X)
G <- res_load$G
G_dim <- as.vector(res_load$r_hat)

candidates <- cand_sbs(G, G_dim, single = FALSE)
TNotSBS(G, G_dim, method = c("oracle"), m = 3)

```




# other types of change

```{r}
# single row loading change
set.seed(NULL)
res_rl <- dgp_general(
  model= "matrix",
  dim_obs = c(100, 100),
  dim_latent = c(4, 3),
  Time = 500,
  coeff = 0.7,
  true_cp = 250,
  type_mode = list(c(1)),
  type_change = list("l"),
  shift_ind = list(list(c(80,2))),
  shift_mean = c(0),
  shift_var = c(2^2)
)

```

```{r}
# single column loading change
res_cl <- dgp_general(
  model= "matrix",
  dim_obs = c(100, 100),
  dim_latent = c(4, 3),
  Time = 500,
  coeff = 0.7,
  true_cp = 250,
  type_mode = list(c(2)),
  type_change = list("l"),
  shift_ind = list(list(NULL,c(80,2))),
  shift_mean = c(0),
  shift_var = c(2^2)
)

```


```{r}
# single row factor change
# set.seed(123)
res_rf <- dgp_general(
  model= "matrix",
  dim_obs = c(100, 100),
  dim_latent = c(4, 3),
  Time = 500,
  coeff = 0.7,
  true_cp = 250,
  type_mode = list(c(1)),
  type_change = list("f"),
  add_factors = list(c(2, 0)),             # Add 2 row factors
  add_factors_coeff = list(c(0.5, 0)) 
)



```

